SMT-Boosted Security Types for Low-Level MPC

### 2025-11-24 toplas26/lang.tex
checkpoint

The $\minifed$ language establishes a basic model of synchronous
protocols between a federation of \emph{clients} exchanging values in
the binary field. We identify clients by natural numbers and federations- finite sets of
clients- are always given statically.  Our threat model assumes a
partition of the federation into \emph{honest} $H$ and \emph{corrupt}
$C$ subsets. We model probabilistic programming via a \emph{random
tape} semantics. That is, we will assume that programs can make
reference to values chosen from a uniform random distributions defined
in the initial program memory.  Programs aka protocols execute
deterministically given the random tape.

@@

\paragraph{Sanity conditions on protocols} To simplify
the presentation we will disregard protocols that are semantically
ill-defined. That is, we generally assume that for any
configuration $(\store, \prog)$ there exists $\store$
with $(\store, \prog) \redxs \store$. This rules out
use of undefined variables and, in the adversarial semantics,
programs consisting of just a failing $\assert$.

>>>>

The $\minifed$ language establishes a basic model of synchronous
protocols between a federation of \emph{clients} exchanging values in
a finite field. In order to align with existing SMT theories
\cite{SMFF} we restrict our consideration to prime fields. We identify
clients by natural numbers and federations- finite sets of clients-
are always given statically.  Our threat model assumes a partition of
the federation into \emph{honest} $H$ and \emph{corrupt} $C$
subsets. We model probabilistic programming via a random tape
semantics. That is, we will assume that programs can make reference to
values chosen from a uniform random distributions defined in the
initial program memory.  Programs aka protocols execute
deterministically given the random tape.

@@

\paragraph{Sanity conditions on protocols} To simplify
the presentation we will disregard protocols that are semantically
ill-defined. That is, we generally assume that for any
program $\prog$ there exists $\store$
with $(\store, \prog) \redxs \store$. This rules out
use of undefined variables and, in the adversarial semantics,
programs consisting of just a failing $\assert$.
